quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-15 paper-quollr.Rmd
Add algorithm steps latex output

@@

@@

@@

@@

```{r, eval=knitr::is_latex_output()}
scurve_umap_plt + hex_grid_poly_scurve + 
  hex_centroids_scurve + wireframe_scurve + 
  plot_layout(ncol = 5)
```

>>>>

scurve_umap_plt_int <- ggplotly(scurve_umap_plt, 
                                width = "350", 
                                height = "350", 
                                tooltip = "none") |>
  config(
    staticPlot = TRUE,        # Disables all interactivity (no hover, zoom, pan)
    displayModeBar = FALSE,   # Hides the plotly toolbar
    editable = FALSE,         # Disables annotations and editing
    showTips = FALSE,         # Removes tooltip on hover
    displaylogo = FALSE,      # Hides plotly logo
    responsive = FALSE        # Disables responsive resizing
  )

@@

hex_grid_poly_scurve_int <- ggplotly(hex_grid_poly_scurve, 
                                width = "350", 
                                height = "350", 
                                tooltip = "none") |>
  config(
    staticPlot = TRUE,        # Disables all interactivity (no hover, zoom, pan)
    displayModeBar = FALSE,   # Hides the plotly toolbar
    editable = FALSE,         # Disables annotations and editing
    showTips = FALSE,         # Removes tooltip on hover
    displaylogo = FALSE,      # Hides plotly logo
    responsive = FALSE        # Disables responsive resizing
  )

@@

hex_centroids_scurve_int <- ggplotly(hex_centroids_scurve, 
                                width = "350", 
                                height = "350", 
                                tooltip = "none") |>
  config(
    staticPlot = TRUE,        # Disables all interactivity (no hover, zoom, pan)
    displayModeBar = FALSE,   # Hides the plotly toolbar
    editable = FALSE,         # Disables annotations and editing
    showTips = FALSE,         # Removes tooltip on hover
    displaylogo = FALSE,      # Hides plotly logo
    responsive = FALSE        # Disables responsive resizing
  )

@@

wireframe_scurve_int <- ggplotly(wireframe_scurve, 
                                width = "350", 
                                height = "350", 
                                tooltip = "none") |>
  config(
    staticPlot = TRUE,        # Disables all interactivity (no hover, zoom, pan)
    displayModeBar = FALSE,   # Hides the plotly toolbar
    editable = FALSE,         # Disables annotations and editing
    showTips = FALSE,         # Removes tooltip on hover
    displaylogo = FALSE,      # Hides plotly logo
    responsive = FALSE        # Disables responsive resizing
  )

@@

crosstalk::bscols(
    htmltools::div(style="display: grid; grid-template-columns: 1fr 1fr;",
                   scurve_umap_plt_int, hex_grid_poly_scurve_int,
                   hex_centroids_scurve_int, wireframe_scurve_int, 
                    htmltools::div(
                      style = "margin-top: 13px;",  # adjust px as needed
                      scurve_umap_model_vis
                    )),
    device = "xs"
  )
```

```{r, eval=knitr::is_latex_output(), out.width="100%"}
scurve_umap_plt + hex_grid_poly_scurve +
  scurve_proj_umap_model1 + scurve_proj_umap_model2 +
  hex_centroids_scurve + wireframe_scurve + 
  scurve_proj_umap_model3 + scurve_proj_umap_model4 +
  plot_layout(ncol = 4)
```
